\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Brainstorm}

\begin{document}

\maketitle

\subsection*{5 ideas of final projects}
The following was pushed to repository \url{https://github.com/ru-engineering/group-project-mech1-04}
\subsubsection*{1. Sun-finder for solar-cells}
Using the servo motor a mounted solar-cell can be actuated to angle the sun at the most direct angle for highest yield. In order to find the sun in the sky the light dependant resistor parallel to the solar cell will be used as an input to scan for intensity of light and turn the rotor to face highest intensity. 
\subsubsection*{2. Automated cocktail maker}
A simple liquid pump can be used to pump drinks up a tube, if the pump is using a servo motor each rotation of the pump can be calibrated to a volume of liquid per rotation. If the pump moves the liquid to a funnel that mixes the liquid together. The pi will monitor amount of liquid pumped according to programmed recipes. An LCD will be used to show pouring process. A button will allow user to cycle through few cocktails in order to pick what the user wants


\subsubsection*{3. Smart mirror - With coffee maker}
For this project we will need Raspberry Pi with a Wi-Fi adapter, micro SD Card
and HDMI monitor which will be the screen of the smart mirror. Two-way mirror or one-way reflective film and a frame.
Then a water pump and heater will be controlled using the pi to make coffee at a predetermined time or with a voice command.
%https://maker.pro/raspberry-pi/projects/how-to-create-a-smart-mirror-using-raspberry-pi-and-magic-mirror
\subsubsection*{4. Surveillance robot}
Robot-car with a mounted camera that navigates a room and records according to a path. Needs to use relays and a battery pack to power the DC motors to drive the car. Sonar sensor can be utilized to get a sense of the room in order to navigate the room without running into things. The video will be saved onto the sd card. Then a script will upload the video to a remote location and wipe from the sd card. 
\subsubsection*{5. Candy cannon}
With the usage of motors there will be several boxes with different types of candy. When the user chooses a candy of its own choice a motor will push the candy down onto a platform that has a compressed spring. The spring will have to be connected to motor that will compress it when the user choices a candy and when the candy drops onto the platform it will launch out the candy to the user through a cannon or some kind of tube.
\end{document}
